%------------------------
% Resume Template
% Author : Abhishek Oraon
% Github : https://github.com/DaaSH23
% License : Open Sourced (Do whatever you want)
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Abhishek Oraon}} & Email: \href{mailto:}{reachtoabhisheko@gmail.com}\\
   & Mobile:~~~9748926012 \\
  \href{https://github.com/DaaSH23}{Github: ~~github.com/DaaSH23} \\     \href{https://www.linkedin.com/in/abhishek-oraon-developer/}{@Linkedin}  
 \href{https://daash23.github.io/abhishekO-portfolio/}{~~@Website}
\end{tabular*}

\vspace{-4pt}


%----------SKILLS-----------------
\section{Skills Summary}
\vspace{2pt}
	\resumeSubHeadingListStart
%EditedPartStart
\resumeSubItem{Languages}{~~~~~~~~~~~~~~~JavaScript, C++/C, SQL, HTML, CSS, Python}
\resumeSubItem{Frameworks}{~~~~~~~~~~~~~Node.js, Express.js, React.js, Next.js, .NET Core MVC, Bootstrap, Tailwind, jQuery, Redux}
\resumeSubItem{Databases}{~~~~~~~~~~~~~~~SQL Server, PostgreSQL, MySQL, MongoDB}
\resumeSubItem{Tech/Cloud tools}{~~~~~Git, Visual Studios, Figma, AWS S3}
%EditedPartEnd
\resumeSubHeadingListEnd
\vspace{-5pt}


%----------EXPERIENCE-----------------
\section{Experience}
\vspace{1pt}
  \resumeSubHeadingListStart
 
    \resumeSubheading{\href{https://drive.google.com/file/d/1bftQ4Yxv-49EjjiuvKtFl_dubpLgzF_I/view?usp=sharing}{Digital Resonance Pvt Ltd.}}{Kolkata}
	{Software Developer (Intern)}{June 2023 - Mar 2024}
	\resumeItemListStart
 
        \resumeItem{Adamas Tech Consulting (Contractual Employee)}{(On-Site) Software Engineer on behalf of Digital Resonance Pvt Ltd. Aug 2023 - Mar 2024}
	\resumeItemListStart
        \resumeItem{}{Led the development of comprehensive services for the Student Management System by employing \textbf{C\#}, \textbf{ASP.NET Core MVC}, \textbf{JQuery}, and \textbf{SQL Server} Database. Implemented automation processes that cut data processing and feeding time by \textbf{40\%}}
        \resumeItem{}{Collaborated with a cross-functional team to ensure seamless integration between front-end and back-end components.}
        \resumeItem{}{Contributed to the design and implementation of \textbf{user-friendly} interfaces for efficient student data management.}
	\resumeItemListEnd

        \vspace{5pt}

        \resumeItem{Asset Tracking Management, ERP}{June 2023 - Aug 2023}
	\resumeItemListStart
        \resumeItem{}{Led the development of \textbf{API} services for Asset Tracking Management, ERP, using \textbf{C\#}, \textbf{ASP.NET framework}, and \textbf{SQL Server} database. resulting in a \textbf{35\%} improvement in system performance.}
        \resumeItem{}{Implemented \textbf{RFID} technology to facilitate efficient asset tracking, contributing to streamlined asset management processes.}
        \resumeItem{}{Played a key role in enhancing the \textbf{overall functionality} and reliability of the Asset Tracking Management system.}
	\resumeItemListEnd
% \vspace{5pt}
\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\vspace{-10pt}
\section{Projects}
\resumeSubHeadingListStart
\vspace{1pt}

%\resumeSubItem{VoiceCode - Collaborative code editor (Web Development)}{Created a collaborative coding platform using React.js, Node.js, MongoDB, and Express.js. Implemented a real-time Visual Studio Code editor for multiple users to collaborate on coding projects. Users can save their progress, compile code, and work together seamlessly. Responsible for developing front-end in React.js [ Project ongoing ] \hspace{290pt}(June 2023)}

\resumeItem{NPM packages}{Build global packages to help ease down the development process(Aug 2024)}
	\resumeItemListStart
        \resumeItem{}{\href{https://www.npmjs.com/package/cli-task-tracker}{(cli-task-tracker)}- task management, helps to manage task and list down the todos on your cli. That runs on top of \textbf{Node.js}, \textbf{Chalk-animation}, \textbf{js}. }
        \resumeItem{}{\href{https://www.npmjs.com/package/react-loadscreen-ui}{(react-load-ui)} - customizable React component for creating engaging loading screens. It provides a seamless way to display load screens with various styles, making it easy to enhance the user experience in your React applications. Build using \textbf{Vite} environment, \textbf{React.js}, \textbf{ContextAPI}, \textbf{typescript}}
	\resumeItemListEnd
\vspace{5pt}
\resumeSubItem{\href{https://github.com/DaaSH23/QPportal}{Question Paper Management Portal} - Website for question papers management (Web Development)}{Developed a comprehensive web portal to manage \textbf{question papers} and \textbf{study notes}, providing students easy access to previous years' papers and notes. The portal includes an \textbf{admin panel} for teachers to upload, manage, and organize question papers and study notes. Tools used: \textbf{React.js}, \textbf{ContextAPI}, \textbf{Tailwind}, \textbf{Node.js}, \textbf{Express.js}, \textbf{MongoDB}, \textbf{AWS S3}. (Jan 2024)}
\vspace{5pt}
\resumeSubItem{\href{https://github.com/DaaSH23/Password-gen-extension}{Password Generator Chrome Extension }}{Built a user-friendly website for generating secure passwords, customizable based on user preferences. Additionally, developed a \textbf{Chrome extension} to facilitate seamless password generation during sign-up processes. Tools used: \textbf{JavaScript}, html, css. (May 2022)}
\vspace{5pt}
\resumeSubItem{\href{https://github.com/DaaSH23/mini-game-abhishekO}{ Web-Based Mini Games }- Web based mini games (Web Development)}{Created a collection of web-based \textbf{mini games}, including a \textbf{Simon's game} and \textbf{pattern-based} memory games, aimed at serving as brain-teasers and memory boosters. Tools used: \textbf{html}, \textbf{css}, \textbf{JavaScript}. (Feb 2022)}
% \vspace{1pt}
% \resumeSubItem{\href{https://github.com/DaaSH23/Weather-web}{ \href{https://github.com/DaaSH23/Weather-web\%7D\%7BWeather}{Weather} Information Website } - Weather Website (Web Development)}{Designed a weather information website that integrates the OpenWeather API to provide accurate weather details for user-specified locations. Employed Node.js, Express.js, and API calls for fetching real-time data. Tools used: Node.js, Express.js, OpenWeather API.  \hspace{35pt}(Jul 2022)}


\vspace{3pt}
\resumeSubHeadingListEnd
\vspace{-5pt}


%-----------EDUCATION-----------------
\section{Education}
\vspace{1pt}
  \resumeSubHeadingListStart
    \resumeSubItem
      {Government College Of Engineering and Ceramic Technology (Kolkata, India)
       Bachelor of Technology - Information Technology;  CGPA: 9.29 (2024)}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Object-oriented programming (OOP), Operating System (OS), Data Structures Algorithm (DSA), Networking, Database.}}}
\vspace{5pt}
    \resumeSubItem
      {Techno India Group Public School (Hooghly, India)}
      {Higher Secondary Examination - PCM(+computer)
     CGPA: 7.1 (2019)}
    \resumeSubHeadingListEnd
    \vspace{-4pt}


%------------AWARDS-----------------
\section{Certification}
\vspace{1pt}
\begin{description}[font=$\bullet$]
\item {\href{https://drive.google.com/file/d/1l4s9oNqg1AFJSN9oxTdcpoJ2ERRSE77T/view?usp=sharing}{Web Designing Beginners Certificate} - Udemy  \hspace{240pt}(May 2022)}
\vspace{-4pt}
\end{description}


%----------VOLUNTEER EXPERIENCE--------
\vspace{-5pt}
\section{Volunteer Experience}
\vspace{1pt}
  \resumeSubHeadingListStart
	\resumeSubItem
    {College Tech Club, Member (Kolkata, India)}
    {Conducted online and offline tech events \&  impacted over 200+ students. Jan 2021 - Apr 2024}
\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubItem
    {Rotaract Club (GCECT), Recruiter (Kolkata, India)}
    {Recruited 100+ members who are willing to contribute to social work, Organized events Jan 2021 - Apr 2024}
\resumeSubHeadingListEnd
\vspace{-5pt}

%----------INTEREST----------
\section{Interests}
\vspace{1pt}
\resumeSubHeadingListStart
\resumeSubItem{Football: Played professionally for sub-division club}{And Represented my school football team as a captain. (2017)}
\vspace{-10pt}
\resumeSubHeadingListEnd
\vspace{5pt}

\end{document}

